### 2016-07-05 text/abstraction_relation.tex
Integrated abstraction relation explanation into the different conditions. Haven't updated the examples yet.

%\item Path conditions onto transformation executions
%\begin{itemize}
%\item Each rule in graph:
%\begin{itemize}
%\item As in paper. Match component is injectively found. Apply component is surjectively found.
%\item For traceability links, PC links are found injectively. Transformation executions links are found surjectively. Not a bijection because multiple rule executions could be present in transformation execution.
%
%\item Question: How to handle unification of matching. Seems to be straightforward before/after must match.
%\end{itemize}
%\end{itemize}

@@

@@

Elements in the iom's Output graph must surjectively match on the Output graph of the PC

@@

Traceability links in the PC must injectively match onto links in the transformation execution. This is to ensure that element creation represented in the path condition reflects actual rule execution present in the transformation execution.

@@

% \cref{def:abstraction_pc_ex} enforces the fact that the matcher part of
% components of the path condition are found through an injective typed graph
% homomorphism in the execution's input model. Additionally, the graph including
% the output of the execution (including traceability information), can be
% mapped by a surjective typed graph homomorphism onto the apply model (plus the
% symbolic traceability links) of the path condition.

\subsubsection{Explanation}

To understand the abstraction relation in \cref{subsubsec:abstraction_relation_formal}, recall
that during the construction of a transformation execution rules are matched
injectively in the input model. This information is present in the first
condition of the abstraction relation (Proposition~\ref{eq:abstr_input_output})
via the injective typed graph homomorphism between the match part of the copies
of rules ``glued'' onto the path condition and the containment transitive
closure of the input part of the transformation execution. This relation
enforces the fact that certain parts of the execution were found, or matched, by
certain parts of the path condition.
On the other hand, the surjection from the output of the execution towards the
apply part of the path condition models the fact that the output of the
execution has been completely built by instantiating the apply parts of the
rules contained in the path condition.

The second condition of the abstraction relation
(Proposition~\ref{eq:abstr_trace}) checks for the fact that symbolic
traceability links in the path condition and traceability links in the execution
correctly correspond to each other. This is modeled by the fact that all
strongly connected components in the path condition, composed only of symbolic
traceability links, are injectively found on the execution. This injection
models the fact that traceability graphs between individual or combined rules in
the path condition are necessarily found in the execution. Note that components
of the path condition are considered because of the fact that disconnected rules
in the path condition may have matched over common elements of a particular
execution. As such, a full injection between the complete traceability graph in
the path condition and the execution would be incorrect. Additionally, in the
second part of Proposition~\ref{eq:abstr_trace} we check the fact that every
traceability link in the execution can be found in the path condition. This
additional sanity check enforces that no spurious traceability links that could
not have been created by the rules present in the path condition exist in the
transformation execution.

Finally, the last clause of the abstraction relation states that rule copies
that are repeated a number of times in the path condition need to be found at
least a similar amount of times in the abstracted transformation execution.

>>>>

@@

The purpose of this relation is to enforce that the path condition accurately represents the elements present in the input model of the transformation execution. Note that extra elements may be present but not matched.

@@

Elements in the iom's Output graph must surjectively match on the Output graph of the PC.

This surjection relation enforces that all elements which have been created in the output of the transformation execution must be represented by the output of the path condition. Note that this matching is from the execution to the path condition. As there may be multiple copies of an element in the execution but the path condition only represents execution of rules once, these elements should match over the same element in the path condition.

@@

Traceability links in the PC must injectively match onto links in the transformation execution using the match function \textit{f}. The purpose of this condition is to ensure that element creation represented in the path condition reflects actual rule execution present in the transformation execution.

Note that again we cannot have two traceability links from the same rule in the path condition matching over a traceability link in the transformation execution. Instead, both traceability links must be uniquely found.

@@
